### 2017-10-24 paper.tex
Removed a random URL
added paragraph on mentoring
related to https://github.com/swcarpentry/collaborative-lesson-development/issues/56

>>>>

In 2015, Software Carpentry established a 'Mentoring Subcommittee' to support instructors as they progressed through training, teaching, curriculum development. The Mentoring Subcommittee has promoted community-building by providing virtual spaces where instructors from all over the world can share success stories and discuss strategies for overcoming challenges. This sharing of expertise and experience between geographically separated instructors has helped strengthen the community around lessons and provides insight into how lessons can be improved (see rule #7).
